\section{Auth Module}

\subsection*{Overview}

The \textbf{Auth} module handles user creation and authentication token validation using the Firebase Admin SDK. It provides a simple REST interface to register new users and verify existing sessions.

\subsection*{Responsibilities}

\begin{itemize}
    \item Creating new users via Firebase.
    \item Verifying ID tokens for secure API access.
    \item Fetching user information by UID.
\end{itemize}

\subsection*{Dependencies}

\begin{itemize}
    \item \texttt{firebase-admin} - for user management and token verification.
    \item \texttt{@nestjs/common} - core NestJS features.
    \item \texttt{class-validator} - request payload validation (via DTO).
\end{itemize}

\subsection*{Main Service Methods}

\begin{itemize}
    \item \textbf{create(dto: CreateUserDto)}: registers a user in Firebase.
    \item \textbf{checkToken(token: string)}: verifies a Firebase ID token.
    \item \textbf{getUserByUid(uid: string)}: fetches user data from Firebase.
\end{itemize}

\subsection*{Testing}

Unit tests are implemented with Jest and cover:
\begin{itemize}
    \item User creation with full name.
    \item Token verification.
    \item User retrieval by UID.
\end{itemize}

\subsection*{Exposed Route}

\subsubsection*{POST /auth/signin}

\begin{tabular}{>{\bfseries}l l}
\toprule
Method & POST \\
Route & /auth/signin \\
Auth required & No \\
Status codes & 201 Created, 400 Bad Request, 500 Internal Server Error \\
\bottomrule
\end{tabular}

\vspace{1em}
\textbf{Request Body:}
\begin{verbatim}
{
  "email": "john@example.com",
  "password": "securePass123",
  "firstname": "John",
  "lastname": "Doe"
}
\end{verbatim}

\vspace{1em}
\textbf{Success Response:}
\begin{verbatim}
Status: 201 Created
{
  "statusCode": 201,
  "message": "User created",
  "data": {
    "uid": "user123",
    ...
  }
}
\end{verbatim}

\vspace{1em}
\textbf{Error Responses:}
\begin{itemize}
    \item \textbf{400 Bad Request} - missing or invalid fields.
    \item \textbf{500 Internal Server Error} - Firebase failure or exception.
\end{itemize}
