\section{Dashboard Module}

\subsection*{Overview}

The \textbf{Dashboard} module provides a synthetic view of a user's activity and data. It aggregates file statistics and coverage request history from Firestore and returns a structured dashboard summary.

\subsection*{Responsibilities}

\begin{itemize}
    \item Aggregate file statistics per user from Cloud Storage.
    \item Count and classify AI coverage requests (pending / completed).
    \item Return a structured summary to the frontend.
\end{itemize}

\subsection*{Dependencies}

\begin{itemize}
    \item \texttt{FileService} - for retrieving user files from storage.
    \item \texttt{Firestore} - for querying the \texttt{coverage\_requests} collection.
    \item \texttt{@nestjs/common} - for DI and controller structure.
\end{itemize}

\subsection*{Main Service Method}

\begin{itemize}
    \item \textbf{buildDashboard(uid: string)}: builds and returns a \texttt{DashboardDto} object containing:
    \begin{itemize}
        \item Total number of user files
        \item Breakdown of files by category
        \item Coverage requests (pending and completed)
        \item Recent request history (max 20)
    \end{itemize}
\end{itemize}

\subsection*{Resilience Handling}

If the required Firestore index is missing, a partial dashboard is returned with empty coverage history. This ensures continued availability even when Firestore is misconfigured.

\subsection*{Exposed Route}

\subsubsection*{GET /dashboard}

\begin{tabular}{>{\bfseries}l l}
\toprule
Method & GET \\
Route & /dashboard \\
Auth required & Yes (via Firebase ID token) \\
Status codes & 200 OK, 500 Internal Server Error \\
\bottomrule
\end{tabular}

\vspace{1em}
\textbf{Headers:}
\begin{verbatim}
Authorization: Bearer <ID_TOKEN>
\end{verbatim}

\vspace{1em}
\textbf{Success Response:}
\begin{verbatim}
Status: 200 OK
{
  "totalFiles": 3,
  "filesByCategory": {
    "health": 1,
    "employment": 2
  },
  "pendingCoverageRequests": 1,
  "completedCoverageRequests": 4,
  "coverageHistory": [
    {
      "requestId": "abc123",
      "prompt": "What is my health coverage?",
      "status": "done",
      "response": "...",
      "updatedAt": 1716170000000
    }
  ]
}
\end{verbatim}

\vspace{1em}
\textbf{Error Responses:}
\begin{itemize}
    \item \textbf{500 Internal Server Error} - Firestore failure or exception.
\end{itemize}
