\section{File Module}

\subsection*{Overview}

The \textbf{FileModule} manages all user file operations including upload, retrieval, deletion, and temporary storage. It integrates Google Cloud Storage via Firebase and uses Pub/Sub to notify other microservices of file-related events.

\subsection*{Responsibilities}

\begin{itemize}
    \item Upload and store user files under structured paths in GCS.
    \item Generate temporary signed URLs for accessing files.
    \item Delete specific or all files for a user.
    \item Notify other services of file upload and deletion via Pub/Sub.
\end{itemize}

\subsection*{Dependencies}

\begin{itemize}
    \item \texttt{@google-cloud/storage} - for GCS bucket access.
    \item \texttt{FirebaseModule} - to inject the GCS bucket.
    \item \texttt{PubSubService} - to publish \texttt{file-upload} and \texttt{file-delete} events.
\end{itemize}

\subsection*{Key Service Methods}

\begin{itemize}
    \item \texttt{uploadFile(uid, file, dto)} - Uploads a categorized file and emits Pub/Sub event.
    \item \texttt{getFileUrl(uid, fileName)} - Returns a temporary signed URL for a user file.
    \item \texttt{getUserFiles(uid)} - Lists all files uploaded by the user.
    \item \texttt{deleteFile(uid, fname, category)} - Deletes a file and emits a Pub/Sub event.
    \item \texttt{deleteAllUserFiles(uid)} - Deletes all user files and emits a single Pub/Sub event.
    \item \texttt{uploadTmpImage(uid, file, dto)} - Special-purpose method to upload temporary images.
    \item \texttt{deleteTempFile(fpath)} - Deletes a temporary file if it exists.
\end{itemize}

\subsection*{Exposed Routes}

\subsubsection*{POST /files/upload}

\begin{tabular}{>{\bfseries}l l}
\toprule
Method & POST \\
Route & /files/upload \\
Auth required & Yes \\
Consumes & multipart/form-data \\
\bottomrule
\end{tabular}

\vspace{1em}
\textbf{Form fields:}
\begin{itemize}
    \item \texttt{file}: PDF file to upload
    \item \texttt{category}: required category label (e.g., \texttt{HEALTH}, \texttt{EMPLOYMENT})
\end{itemize}

\subsubsection*{GET /files/:fileName}

Returns a temporary signed URL for the requested file.

\subsubsection*{GET /files}

Returns a list of all files uploaded by the authenticated user.

\subsubsection*{DELETE /files/:category/:fileName}

Deletes a specific file in a category and emits a \texttt{file-delete} event.

\subsubsection*{DELETE /files}

Deletes all files for the user and emits a single \texttt{file-delete} event.

\subsection*{Error Handling}

\begin{itemize}
    \item \textbf{400 Bad Request} - Invalid or missing category.
    \item \textbf{404 Not Found} - Requested file does not exist.
    \item \textbf{500 Internal Server Error} - Upload/delete/signing failures.
\end{itemize}

\subsection*{Testing}

Unit tests validate:

\begin{itemize}
    \item File upload with event publishing.
    \item Temporary signed URL generation.
    \item Accurate file listing.
    \item Conditional deletion (specific or all files).
    \item Handling of missing files and errors.
\end{itemize}

Mocks are used for:

\begin{itemize}
    \item GCS Bucket and File objects.
    \item Pub/Sub message publishing.
\end{itemize}
