\section{PubSub Module}

\subsection*{Overview}

The \textbf{PubSubModule} encapsulates the Google Cloud Pub/Sub integration used by the application to handle asynchronous communication between microservices. It publishes and subscribes to various event topics related to files and AI coverage analysis.

\subsection*{Responsibilities}

\begin{itemize}
    \item Publish events to specific Pub/Sub topics.
    \item Subscribe to the \texttt{coverage-response-sub} subscription.
    \item Update Firestore with AI coverage results upon message reception.
\end{itemize}

\subsection*{Topics Used}

\begin{itemize}
    \item \textbf{coverage-query} - Trigger coverage analysis requests.
    \item \textbf{coverage-response} - Receives responses from the AI service.
    \item \textbf{file-upload} - Event triggered when a file is uploaded.
    \item \textbf{file-delete} - Event triggered when a file is deleted.
\end{itemize}

\subsection*{Key Methods}

\begin{itemize}
    \item \texttt{publishMessage(topicName: string, data: object)} \\
    Publishes a JSON-encoded message to the specified Pub/Sub topic.

    \item \texttt{subscribeToCoverageResponse()} \\
    Subscribes to \texttt{coverage-response-sub} and processes AI results to update the Firestore \texttt{coverage\_requests} collection.
\end{itemize}

\subsection*{Error Handling}

If a received message is missing expected fields (\texttt{request\_id}, \texttt{user\_uuid}, or \texttt{response}), the message is rejected with \texttt{nack()}. Other exceptions are logged and also result in a negative acknowledgment.

\subsection*{Lifecycle Hook}

The service implements \texttt{OnModuleInit} and only subscribes to incoming Pub/Sub messages if the environment is not \texttt{"test"}. This allows for isolated unit testing without background consumers.

\subsection*{Testing}

Unit tests verify:
\begin{itemize}
    \item That messages are published correctly with expected parameters.
    \item That the \texttt{subscribeToCoverageResponse} method is invoked on module initialization (except in test mode).
    \item That Firestore is updated when a message is handled successfully.
\end{itemize}

Mocks are used for:
\begin{itemize}
    \item Pub/Sub client, topics and subscriptions.
    \item Firestore client and document operations.
\end{itemize}
